%\svnid{$Id: titlepage.tex 43 2013-05-16 16:59:40Z tbrosch $}
\begin{titlepage}
\newlength{\smalltitlespace}
\newlength{\mediumtitlespace}
\newlength{\largetitlespace}
\setlength{\smalltitlespace}{1em}
\setlength{\mediumtitlespace}{1.5em}
\setlength{\largetitlespace}{3.5em}
\noindent
  \begin{center}
  \mbox{}\vfill
  \large\sffamily
  {\huge\bfseries\MakeUppercase{\longtitle}\\}\vspace{2em}
  by\\[1.5em]
  {\Large TOM BROSCH\\[\smalltitlespace]}
  {\Large Dipl.-Ing., Otto-von-Guericke-Universit\"at Magdeburg,
  2010\\[\largetitlespace]}
  {\Large A THESIS SUBMITTED IN PARTIAL
  FULFILLMENT OF\\
  THE REQUIREMENTS FOR THE DEGREE OF\\[\smalltitlespace]
  DOCTOR OF PHILOSOPHY\\[\smalltitlespace]}
  in\\[\smalltitlespace]
  {\Large THE FACULTY OF GRADUATE AND POSTDOCTORAL STUDIES\\[\smalltitlespace]
  (Biomedical Engineering)\\[\largetitlespace]}
  {\Large THE UNIVERSITY OF BRITISH COLUMBIA\\[\smalltitlespace]
  (Vancouver)\\[\largetitlespace]}
  \thesisdate\today\\[\smalltitlespace]
  {\rmfamily \textcopyright{}} Tom Brosch, 2015
  %\vfill
  \end{center}
\end{titlepage}
%\chapter*{Abstract}

\mbox{}\vspace{2em}
\begin{quotation}
\begin{center}
\textbf{Abstract}
\end{center}
\noindent

Deep learning has shown great promise in recent years for various non-medical
and medical problems. However, the size of images has been a burden and problems
had to be mapped to either small 2D or 3D patches, or 2D images. This thesis
analysis the potential of deep learning to solve medical image analysis problems
using entire 3D volumes. A major part of the thesis was the development of a
training method for deep learning models that facilitates the training on entire
3D volumes. We have applied the new training method to solve different medical
image analysis problems, such as manifold learning for biomarker discovery for
AD using raw images, and MS using deformation fields, and lesion masks. A second
part of the thesis was the development of an MS lesion segmentation method using
multimodal MR images. We evaluated the runtime improvements against other
state-of-the-art methods. Furthermore, we showed the clinical value of our
approach on medical problems.

\end{quotation}
\vfill
\noindent
\textbf{Brosch, Tom:}\\
\emph{\longtitle}\\
PhD thesis, The University of British Columbia, 2015